\documentclass{article}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}
\usepackage{indentfirst}

% Signature block creation
\newcommand*{\SignatureAndDate}[2]{%
    \vspace{0.3in}
    \par\noindent\makebox[2.5in]{\hrulefill} \hfill\makebox[2.0in]{\hrulefill}%
    \par\noindent\makebox[2.5in][l]{#1}      \hfill\makebox[2.0in][l]{Date}%
    \vspace{0.3in}
    \par\noindent\makebox[2.5in]{\hrulefill} 
    \par\noindent\makebox[2.5in][l]{Print Signer's Name}  
    \vspace{0.1in}
    \par\noindent\makebox[2.5in][l]{Company Name: #2} 
    \vspace{0.3in} 
}% 

\title{Consulting Agreement}
\author{}

\input{clientinfo.tex}
\input{consultantinfo.tex}

\begin{document}
\maketitle
\section{The Parties}
This Consulting Agreement ("Agreement") is made effective as of \effectivedate by and between:

\textbf{Consultant}: \consultantname with a mailing address of \consultantaddr ("Consultant"),

and

\textbf{Client}: \clientname with a mailing address of \clientaddr

\section{Services}

Consultant agrees to provide the following Services: Engineering design services, product strategy and manufacturability recommendations, etc. ("Services").

\section{Term}

The Services shall commence on \effectivedate , and end: (check one)



\section{Compensation and Payment Method}
In consideration for the Services provided, the consultant will be paid in the following manner.
\begin{itemize}
    \item Hourly Rate for Engineering is \hourlyrate.
    \item Invoices will be sent bi-weekly.
    \item Invoices will have NET 15 terms.
\end{itemize}

\section{Retainer}
The client is not required to pay a Retainer before the Consultant is able to provide services.

\section{Expenses}
\begin{itemize}
    \item The Consultant shall be responsible for all expenses related to providing the Services under this Agreement. This includes, but is not limited to, office supplies, equipment, operating costs, business costs, employment costs, taxes, Social Security contributions and/or payments, disability insurance, unemployment taxes.
    \item The Client shall be responsible for all project-specific expenses incurred in connection with providing the Services.  This may include purchasing of samples, components, project-specific tooling, development kits, printed circuit boards, .  The Client agrees to pay the Consultant for expenses incurred, which will be included in Invoicing. Upon request by the Client, the Consultant will show receipt(s) or proof(s) of purchase for said expense for purchases over \$25. 
\end{itemize}

\section{Travel}
The Client agrees to pay travel expenses incurred by the Consultant in execution of Services.  Travel shall be pre-approved by the Client.  
\begin{itemize}
    \item Hourly Rate: 50\% of Compensation in Section IV of this document for travel time.
    \item Per-Diem cost guidelines: \\ https://www.gsa.gov/travel/plan-book/per-diem-rates/ \\ NOTE: The GSA rates are only guidelines due to high variability of costs, and current costs changing faster than the GSA can update their website.  A reasonable effort will be made to adhere to these guidelines.  
\end{itemize}

\section{Disputes}
If any dispute arises under this Agreement, the Consultant and the Client shall negotiate in good faith to settle such dispute. If the parties cannot resolve such disputes themselves, then either party may submit the dispute to mediation by a mediator approved by both parties. If the parties cannot agree with any mediator or if either party does not wish to abide by any decision of the mediator, they shall submit the dispute to arbitration by any mutually acceptable arbitrator, or the American Arbitration Association (AAA). The costs of the arbitration proceeding shall be borne according to the decision of the arbitrator, who may apportion costs equally or in accordance with any finding of fault or lack of good faith of either party. If either party does not wish to abide by any decision of the arbitrator, they shall submit the dispute to litigation. The jurisdiction for any dispute shall be administered in the County of Los Angeles, State of California.

\section{Legal Notice}
All notices required or permitted under this Agreement shall be in writing and shall be deemed delivered when delivered in-person or deposited in the United States Postal Service via Certified Mail with return receipt. If different from the mailing address in Section I, enter below: \\
Client's Address: \clientaddralt \\
Consultant's Address: \consultantaddralt

\section{Return of Records}
Upon termination of this Agreement, the Consultant shall deliver all records, notes, and data of any nature that are in the Consultant's possession or under the Consultant's control and that are of the Client's property or relate to Client's business.

\section{Waiver of Contractual Right}
The failure of either party to enforce any provision of this Agreement shall not be construed as a waiver or limitation of that party's right to subsequently enforce and compel strict compliance with every provision of this Agreement.

\section{Independent Contractor Status}
The Consultant, under the code of the Internal Revenue (IRS), is an independent contractor and neither the Consultant's employees or contract personnel are, or shall be deemed, the Client's employees. In its capacity as an independent contractor, the Consultant agrees and represents:
\begin{enumerate}
    \item Consultant has the right to perform Services for others during the term of this Agreement;
    \item Consultant has the sole right to control and direct the means, manner, and method by which the Services required under this Agreement will be performed; Consultant shall select the routes taken, starting and ending times, days of work, and order the work that performed;
    \item Consultant has the right to hire assistant(s) as subcontractors or to use employees to provide the Services under this Agreement.
    \item Neither Consultant nor the Consultant's employees or personnel shall be required to wear any uniforms provided by the Client;
    \item The Services required by this Agreement shall be performed by the Consultant, Consultant's employees or personnel, and the Client will not hire, supervise, or pay assistants to help the Consultant;
    \item Neither the Consultant nor the Consultant's employees or personnel shall receive any training from the Client for the professional skills necessary to perform the Services required by this Agreement; and
    \item Neither the Consultant nor Consultant's employees or personnel shall be required by the Client to devote full-time to the performance of the Services required by this Agreement.
\end{enumerate}

\section{State and Federal Licenses}

The Consultant represents and warrants that all employees and personnel associated shall comply with federal, state, and local laws requiring any required licenses, permits, and certificates necessary to perform the Services under this Agreement.

\section{Payment of Taxes}

Under this Agreement, the Client shall not be responsible for:
\begin{itemize}
    \item Withholding FICA, Medicare, Social Security, or any other Federal or State withholding taxes from the Consultant's payments to employees or personnel or make payments on behalf of the Consultant;
    \item Making Federal and/or State unemployment compensation contributions on the Consultant's behalf; and
    \item Making payments of taxes incurred while performing the Services under this Agreement, including all applicable income taxes and, if the Consultant is not a business entity, all applicable self-employment taxes. Upon demand, the Consultant shall provide the Client with proof that such payments have been made.
\end{itemize}

\section{Employee's Compensation}

The Consultant shall be solely responsible for the following:
\begin{itemize}
    \item Employee Benefits. The Consultant understands and agrees that they are solely responsible and shall be liable to all benefits that are provided to their employees, including, but not limited to, retirement plans, health insurance, vacation time-off, sick pay, personal leave, or any other benefit provided.
    \item Unemployment Compensation. The Consultant shall be solely responsible for the unemployment compensation payments on behalf of their employees and personnel. The Consultant shall not be entitled to unemployment compensation with the Services performed under this Agreement.
    \item Workers’ Compensation. The Consultant shall be responsible for providing all workers' compensation insurance on behalf of their employees. If the Consultant hires employees to perform any work under this Agreement, the Consultant agrees to grant workers' compensation coverage to the extent required by law. Upon request by the Client, the Consultant must provide certificates proving workers' compensation insurance at any time during the performance of the Services.
\end{itemize}

\section{Indemnification}

Consultant shall release, defend, indemnify, and hold harmless Client and its officers, agents, and employees from all suits, actions, or claims of any character, name, or description including reasonable Consultant fees, brought on account of any injuries or damage, or loss (real or alleged) received or sustained by any person, persons, or property, arising out of services provided under this Agreement or Consultant's failure to perform or comply with any requirements of this Agreement including, but not limited to any claims for personal injury, property damage, or infringement of copyright, patent, or other proprietary rights. Client reserves the right to retain whatever funds which would be due to the Consultant under this Agreement until such suits, action or actions, claim or claims for injuries or damages as aforesaid shall have been settled and satisfactory evidence to that effect furnished.

\section{Confidentiality \& Proprietary Information}

The Consultant acknowledges that it will be necessary for the Client to disclose certain confidential and proprietary information to the Consultant in order for the Consultant to perform their duties under this Agreement. The Consultant acknowledges that disclosure to a third (3rd) party or misuse of this proprietary or confidential information would irreparably harm the Client. Accordingly, the Consultant will not disclose or use, either during or after the term of this Agreement, any proprietary or confidential information of the Client without the Client's prior written permission except to the extent necessary to perform the Services on the Client's behalf. 

Proprietary or confidential information includes, but is not limited to:
\begin{enumerate}
    \item The written, printed, graphic, or electronically recorded materials furnished by Client for Consultant to use;
    \item Any written or tangible information stamped "confidential," "proprietary," or with a similar legend, or any information that Client makes reasonable efforts to maintain the secrecy of, business or marketing plans or strategies, customer lists, operating procedures, trade secrets, design formulas, know-how and processes, computer programs and inventories, discoveries and improvements of any kind, sales projections, and pricing information; and
    \item  Information belonging to customers and suppliers of the Client about whom the Consultant gained knowledge as a result of the Consultant‘s Services to the Client.
\end{enumerate}

Upon termination of the Consultant's Services to the Client, or at the Client's request, the Consultant shall deliver all materials to the Client in the Consultant's possession relating to the Client's business. The Consultant acknowledges any breach or threatened breach of confidentiality under this Agreement will result in irreparable harm to the Client for which damages would be an inadequate remedy. Therefore, the Client shall be entitled to equitable relief, including an injunction, in the event of such breach or threatened breach of confidentiality. Such equitable relief shall be in addition to the Client's rights and remedies otherwise available at law.

Furthermore, proprietary information, under this Agreement, shall include:

\begin{enumerate}
    \item The product of all work performed under this Agreement ("Work Product"), including without limitation all notes, reports, documentation, drawings, computer programs, inventions, creations, works, devices, models, works-in-progress and deliverables, will be the sole property of the Client, and Consultant hereby assigns to the Client all right, title, and interest therein, including, but not limited to, all audiovisual, literary, moral rights and other copyrights, patent rights, trade secret rights, and other proprietary rights therein. Consultant retains no right to use the Work Product and agrees not to challenge the validity of the Client's ownership in the Work Product;
    \item Consultant hereby assigns to the Client all right, title, and interest in any and all photographic images and videos or audio recordings made by the Client during Consultant's work for them, including, but not limited to, any royalties, proceeds, or other benefits derived from such photographs or recordings; and
    \item The Client will be entitled to use the Consultant's name and/or likeness in advertising and other materials.
\end{enumerate}

\section{Assignment and Delegation}

The Consultant may assign rights and may delegate duties under this Agreement to other individuals or entities acting as a subcontractor ("Subcontractor"). The Consultant recognizes that they shall be liable for all work performed by the Subcontractor and shall hold the Client harmless of any liability in connection with their performed work.

The Consultant shall be responsible for any confidential or proprietary information that is shared with the Subcontractor in accordance with this section. If any such information is shared by the Subcontractor to third (3rd) parties, the Consultant shall be made liable.

\section{Governing Law}

This Agreement shall be governed under the laws in the State of California.

\section{Severability}

This Agreement shall remain in effect in the event a section or provision is unenforceable or invalid. All remaining sections and provisions shall be deemed legally binding unless a court administers that any such provision or section is invalid or unenforceable, thus, limiting the effect of another provision or section. In such a case, the affected provision or section shall be enforced as so limited.

\section{Additional Terms \& Conditions}

None.

\section{Entire Agreement}

This Agreement, along with any attachments or addendums, represents the entire agreement between the parties. Therefore, this Agreement supersedes any prior agreements, promises, conditions, or understandings between the Client and Consultant. This Agreement may be modified or amended if the amendment is made in writing and is signed by both parties.

\newpage
\section{Signatures}

\textbf{Consultant Signature}

\SignatureAndDate{Company Representative}{\consultantname}

\textbf{Client Signature}
\SignatureAndDate{Client Representative}{\clientname }


\end{document}
